---
title: "General Overview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# General Overview

The MicrobDateTools package was develloped as a set of tools to standardize microbial 'omics datasets. 

There are xx set of functions

## 1. Downloading data
download.sequences.INSDC
get.BioProject.metadata.INSDC
get.sample.attributes.INSDC

## 2. Data quality controll
dataQC.completeTaxaNamesFromRegistery
dataQC.dateCheck  
dataQC.LatitudeLongitudeCheck
dataQC.taxaNames
dataQC.TermsCheck

dataQC.eventStructure
dataQC.generate.footprintWKT
dataQC.guess.env_package.from.data

dataQC.findNames
dataQC.TaxonListFromData

## 3. Data standardisation
dataQC.MIxS
dataQC.DwC
dataQC.DwC_general

commonTax.to.NCBI.TaxID
coordinate.to.decimal

## 4 upload data
sync.metadata.sequenceFiles
prep.metadata.ENA
rename.sequenceFiles
FileNames.to.Table

## 5. Data objects and validation
check.valid.metadata.DwC
check.valid.metadata.MIxS



## 6. data help
get.boundingBox
get.insertSize

get.ENAName
term.definition

## 7. data formtting manipulation
combine.data
combine.data.frame
eMoF.to.wideTable
wideTable.to.eMoF
wideTab.to.hierarchicalTab

## 8. Data Libraries       
ENA_allowed_terms
ENA_checklistAccession
ENA_instrument
ENA_geoloc
ENA_select
ENA_strat
TaxIDLib

MarsLib

TermsSyn
TermsLib
TermsSyn_DwC
   

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MicrobeDataTools)
```
